Bibat: Batteries-include Bayesian Analysis Template

### 2024-02-15 paper/main.tex
Update paper

Bibat integrates many widely-adopted, open-source and powerful tools to
implement the components of a Bayesian workflow. Bibat projects are is
written in modern Python and uses pydantic Pydantic developers (2022)
and pandera (Niels Bantilan 2020) for data modelling, Stan (Carpenter et
al. 2017) for statistical inference, cmdstanpy (Stan Development Team
2022) for python-Stan interface, arviz (Kumar et al. 2019) for storing
and analyzing inferences and sphinx (Georg Brandl and the Sphinx team
2022) and quarto (Allaire et al. 2022) for documentation. Bibat itself
is also written in modern Python and uses the popular tools cookiecutter
(Greenfeld et al. 2021), pydantic and click (Click Developers 2022).

To encourage collaborative development of Bayesian workflow projects,
Bibat projects include a preconfigured test environment, continuous
integration, linting and pre-commit hooks. In addition, including
documentation as a first class component of the analysis addresses a
common problem in academic statistics projects where the paper gets out
of sync with the code. Bibat itself is continuously tested to ensure
that it works on the operating systems Linux, macOS and Windows. Bibat's
continuous integration runs a test suite as well as an end-to-end
functional test on all supported Python versions.

@@

Bibat is developed in public and encourages community contribution.
Please see the contributing page
\url{https://github.com/teddygroves/bibat/blob/main/CONTRIBUTING.rst}
and code of conduct
\url{https://github.com/teddygroves/bibat/blob/main/CODE_OF_CONDUCT.md}
if you would like to help develop bibat.

@@

\bibitem[\citeproctext]{ref-clickdevelopersClickPythonComposable2022}
Click Developers. 2022. {``Click: {Python} Composable Command Line
Interface Toolkit.''} Pallets. \url{https://pypi.org/project/click/}.

@@

\bibitem[\citeproctext]{ref-greenfeldCookiecutter2021}
Greenfeld, Audrey Roy, Dainiel Roy Greenfeld, Raphael Pierzina, et al.
2021. {``Cookiecutter.''} \url{https://pypi.org/project/cookiecutter/}.

>>>>

Bibat integrates many widely-adopted, open-source and powerful tools to
implement the components of a Bayesian workflow. Bibat projects are
written in modern Python and uses pydantic (Pydantic developers 2022)
and pandera (Niels Bantilan 2020) for data modelling, Stan (Carpenter et
al. 2017) for statistical inference, cmdstanpy (Stan Development Team
2022) for python-Stan interface, arviz (Kumar et al. 2019) for storing
and analyzing inferences and sphinx (Georg Brandl and the Sphinx team
2022) and quarto (Allaire et al. 2022) for documentation. Bibat itself
is also written in modern Python and uses the previously mentioned
software as well as the popular popular template tool copier (copier
developers 2024).

To encourage collaborative development of Bayesian workflow projects,
Bibat projects include a preconfigured test environment, continuous
integration, linting and pre-commit hooks. In addition, including
documentation as a first class component of the analysis addresses a
common problem in academic statistics projects where the paper gets out
of sync with the code. Bibat is continuously tested to ensure that it
works on the operating systems Linux, macOS and Windows. Bibat's
continuous integration runs a test suite as well as an end-to-end
functional test on all supported Python versions.

@@

Bibat is developed in public and encourages community contribution.
Please see the contributing page
\url{https://github.com/teddygroves/bibat/blob/main/CONTRIBUTING.md} and
code of conduct
\url{https://github.com/teddygroves/bibat/blob/main/CODE_OF_CONDUCT.md}
if you would like to help develop bibat.

@@

\bibitem[\citeproctext]{ref-copierdevelopersCopier2024}
copier developers. 2024. {``Copier.''} copier-org.
\url{https://github.com/copier-org/copier}.

@@
